---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# immunoeasy

<!-- badges: start -->
<!-- badges: end -->

The goal of immunoeasy is to make immunologist life easier with clear functions. 

## Installation

You can install the released version of immunoeasy from [Github](https://github.com/itamuria/immunoeasy) with:

``` r

# library(devtools)
# devtools::install_github("itamuria/immunoeasy")
library(remotes)
remotes::install_github("itamuria/immunoeasy")
```

## Obtain information

If we want to know information about an ensemble id we can use the ens2symbol function. For example if we want to know the information about ENSG00000000003 we should do in the next way:



```{r example}
library(immunoeasy)
## basic example code

ens2symbol(ens_ids = c("ENSG00000000003"))




```

### Load package and data

The data can be loaded from github or can be found in the package dataset. 

```{r}
rm(list = ls())
time_doc1 <- Sys.time()
library(immunoeasy)
if (!require("pacman")) install.packages("pacman")
library(pacman)
pacman::p_load(ggplot2, repmis,RColorBrewer,SuperLearner, gam,splines,foreach,glmnet,Matrix,nnet,polspline,e1071,xgboost)
# Download data
source_data("https://github.com/itamuria/expose_dataset/blob/master/20180818_dtaset.RData?raw=true")
set.seed(22222)
```

