---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# immunoeasy

<!-- badges: start -->
<!-- badges: end -->

The goal of immunoeasy is to make immunologist life easier with clear functions. 

## Installation

You can install the released version of immunoeasy from [Github](https://github.com/itamuria/immunoeasy) with:

``` r

# library(devtools)
# devtools::install_github("itamuria/immunoeasy")
library(remotes)
remotes::install_github("itamuria/immunoeasy")
```

## Obtain information

If we want to know information about an ensemble id we can use the ens2symbol function. For example if we want to know the information about ENSG00000000003 we should do in the next way:



```{r example}
library(immunoeasy)
library(knitr)
library(dplyr)
library(kableExtra)
## basic example code

example_ensg <- ens2symbol(ens_ids = c("ENSG00000000003","ENSG00000184389"))

example_ensg %>% 
    kable() %>%
    kable_styling()


```

### From counts to fpkm from htseq files

If we have the htseq file and we want to obtain the fpmk and cuartiles. mfl_number is the average size of the reads. In this case it is 569.

```{r count2fpkm_htseq}

repmis::source_data("https://github.com/itamuria/immunoeasy/blob/master/data/immunoeasy_counts.RData?raw=true")

names(count_list)

for(c in 1:length(count_list))
{
  if(c == 4) 
  {
    write.table(count_list[[c]], file = paste0(names(count_list)[c],".txt"),row.names = FALSE, sep = "\t")
  } else if(c == 2)  
    {
    write.table(count_list[[c]], file = paste0(names(count_list)[c],".txt"))
    }
  else {
    write.table(count_list[[c]], file = paste0(names(count_list)[c],".txt"),row.names = FALSE)
  }
}

biomartCacheClear() 
htseq_fpkm <- counts2fpkm_htseq (filename = "htseq_counts.txt", mfl_num = c(569))

```

### From counts to fpkm from quant3 files

If we have the htseq file and we want to obtain the fpmk and cuartiles. mfl_number is the average size of the reads. In this case it is 569.

```{r count2fpkm_quant3}


quant_fpkm <- counts2fpkm_quant (filename = "quant_counts.txt", mfl_num = c(569))


```

### From counts to fpkm from subread files

If we have the htseq file and we want to obtain the fpmk and cuartiles. mfl_number is the average size of the reads. In this case it is 569.

```{r count2fpkm_subread}

subread_fpkm <- counts2fpkm_subread (filename = "subread_counts.txt", mfl_num = c(569))


```


### From counts to fpkm from cuff files

If we have the htseq file and we want to obtain the fpmk and cuartiles. mfl_number is the average size of the reads. In this case it is 569.

```{r count2fpkm_cuff, previous_clean = TRUE}

cuff_fpkm <- counts2fpkm_cuff (filename = "cufflink_fpkm.txt", previous_clean = TRUE)

```
